Retirement Consumption: Evidence from UK Pension Reform

### 2024-11-23 Texfiles/5348H.tex
Update regression equations

An individual is defined as treated if they retired between and including 2015 and 2017, and an individual is in the control group if they retired in 2014 or earlier.
Since I am interested in consumption in early retirement, an individuals interview date needs to be within the first three years of them retiring.

@@

I use consumption data of individuals up to 3 years into their retirement so
that the sample size is larger. So, if someone retired in 2015 and had
consumption data in 2015 and 2017, I include both values.

>>>>

An individual is defined as treated if they retired between and including 2015 and 2017, and an individual is in the control group if they retired in 2014 or earlier. I use retirement year relative to 2014 as the running variable, and restrict the bandwidth to 3 years.

@@
